---
title: "BGC Manual"
subtitle: "v.`r SpaDES.core::moduleMetadata(module = 'BGC', path = '..')$version`"
date: "Last updated: `r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    theme: sandstone
    number_sections: false
    df_print: paged
    keep_md: yes
editor_options:
  chunk_output_type: console
  bibliography: citations/references_BGC.bib
link-citations: true
always_allow_html: true
---

# BGC Module

<!-- the following are text references used in captions for LaTeX compatibility -->
(ref:BGC) *BGC*

```{r setup-BGC, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## change to eval = TRUE if all chunks are to be evaluated
```

<!-- if knitting to pdf remember to add the pandoc_args: ["--extract-media", "."] option to yml in order to get the badge images -->

#### Authors:

`r paste(as.character(SpaDES.core::moduleMetadata(module = "BGC", path = '..')$authors), sep = ', ')`
<!-- ideally separate authors with new lines, '\n' not working -->

## Module Overview

### Module summary

Provide a brief summary of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

### Module inputs and parameters

sufficient.
Table \@ref(tab:moduleInputs-BGC) shows the full list of module inputs.

```{r moduleInputs-BGC, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_inputs <- SpaDES.core::moduleInputs("BGC", "..")
knitr::kable(df_inputs,
             caption = "List of (ref:BGC) input objects and their description.") |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

Table \@ref(tab:moduleParams-BGC) shows the full list of module parameters.

```{r moduleParams-BGC, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_params <- SpaDES.core::moduleParams("BGC", "..")
knitr::kable(df_params, caption = "List of (ref:BGC) parameters and their description.") |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

### Events

Describe what happens for each event type.

### Plotting

Write what is plotted.

### Saving

Write what is saved.

### Module outputs

Description of the module outputs (Table \@ref(tab:moduleOutputs-BGC)).

```{r moduleOutputs-BGC, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
df_outputs <- SpaDES.core::moduleOutputs("BGC", "..")
knitr::kable(df_outputs, caption = "List of (ref:BGC) outputs and their description.") |>
  kableExtra::kable_styling(latex_options = "scale_down", full_width = TRUE)
```

### Links to other modules

Describe any anticipated linkages to other modules, such as modules that supply input data or do post-hoc analysis.

### Getting help

- <https://github.com/PredictiveEcology/BGC/issues>
